
\section{Versions released in 2004 (16)}
\subsection*{0.0.9.3 r1.14 beta 9 (Dec/04/2004)}
\begin{itemize}
  \item Bug(s) fixed:
    \begin{itemize}
      \item Fixed a bug that caused \RR{} GUI window to shrink or expand to a certain size,
        whenever code was submitted to Rgui in MDI mode: thanks \texttt{Steven}!
      \item Small bug with the function SEND FILE fixed when the file is set READ ONLY.
    \end{itemize}
  \item For a while, it is strongly recommended to set the BACKGROUND COLOR of ALL SUPPORTED LANGUAGES to WHITE.
  \item The defaults Delphi dialogs were replaced by a new, free and good suite of components called psvDialogs
    written by \texttt{Serhiy Perevoznyk}. Thanks \texttt{Serhiy}! So, the Dialogs are now more pretty.
  \item Add menu \textit{Format/Block/Uncomment first occurrence}.
  \item Search/Replace was improved with the solution proposed for the 0.0.9.0 r1.09 issue. The user can now work
    in all windows (even horizontally or vertically splitted): thanks the Tinn Team.
  \item The user can now work in all window (even horizontally or vertically splitted) for comment/uncomment blocks.
  \item The syntax selector on file load was reworked.
  \item Added \textit{C\# highlighter} instead of that mocked up Java one I had been using like a fool.
  \item The necessary option \texttt{options(debug.catfile = 'stdout')} related to the package \textttt{debug}
   will be automatically sent to the \RR{} interpreter from this version.
\end{itemize}


\subsection*{0.0.9.2 r1.14 beta 8 (Oct/2004)}
\begin{itemize}
  \item Menu \textit{R$\backslash$Show} and \textit{Hide \RR{} Toolbar} was eliminated. This option is changed
    to \textit{View$\backslash$Toolbars$\backslash$R} with others toolbars. It is a more logic place for this option.
  \item Menu \textit{Editor: line below and top} was replaced by \textit{Editor: Current line to top}.
    This improves work alternate with \textit{Send: Line to end page} and \textit{Editor: Current line to top}.
  \item The send line code was improved.
  \item The component SK donated by MJT Net was replaced by the sndKeys32.pas written by Ken Henderson
    and adapted for use in Tinn-R. This change impacts all send and controlling \RR{} function.
\end{itemize}


\subsection*{0.0.9.1 r1.14 beta 7 (Oct/2004)}
\begin{itemize}
  \item Bug(s) fixed:
    \begin{itemize}
      \item Minor bug with menu \textit{R/Controlling R} (enabled/disabled) was corrected.
    \end{itemize}
  \item Tinn and Tinn-R can now run together.
\end{itemize}


\subsection*{0.0.9.1 r1.14 beta 6 (Sep/2004)}
\begin{itemize}
  \item Bug(s) fixed:
    \begin{itemize}
      \item Minor bugs with general appearance (LikeXP, unlike XP) were corrected.
    \end{itemize}
  \item Marco de Groot (Mattic Software), old Tinn developer, is the new co-author of the Tinn-R: welcome Marco!
  \item Backup and restore were reworked: now the user can choose the directory.
  \item Tinn-R is now more user-friendly to run with R: better \RR{} open/save dialogs.
  \item Save file interface was reworked: \RR{} files (*.r; *.q) is now the primary option.
  \item Open file interface was reworked: the three major file extensions are now the first one available:
    \begin{enumerate}
      \item \RR{} files (*.r; *.q);
      \item Text Files (*.txt);
      \item All files (*.*).
    \end{enumerate}
  \item Add menu \textit{Help/FAQ}.
  \item Delays in large files were corrected: thank you Marco de Groot.
  \item \textit{About} was reworked: mails of all authors are now included.
\end{itemize}


\subsection*{0.0.9.0 r1.14 beta 5 (Sep/2004)}
\begin{itemize}
  \item Bug(s) fixed:
    \begin{itemize}
      \item A small bug in resizing the gutter (respect to autoSize and bookmarks) was corrected.
      \item A bug with bracket colors was corrected: it eliminated the bracket background when
        the active line highlighting is set to off.
    \end{itemize}
  \item General stability was improved.
  \item Appearance was relooked.
\end{itemize}


\subsection*{0.0.9.0 r1.14 beta 4 (Aug/2004)}
\begin{itemize}
  \item A tooltip was missing in the \textit{search in files} toolbar button.
  \item New tools to save/restore configuration files for Tinn-R are now added.
\end{itemize}


\subsection*{0.0.9.0 r1.14 (Aug/2004)}
\begin{itemize}
  \item Bug(s) fixed:
    \begin{itemize}
      \item A bug when \RR{} and a graph device are maximized and the latter had the
        focus is now fixed (nothing happened in this case when sending data from
        Tinn-R to R).

        \begin{footnotesize}
          \begin{verbatim}
            Note: Tinn-R 0.0.9.0 r1.13 is now frozen and goes through a wider beta test
            Tinn-R 0.0.9.0 r1.14 and over are considered development versions; they may
            possibly show some instabilities during development.
          \end{verbatim}
        \end{footnotesize}

    \end{itemize}
  \item Specific \RR{} hotkeys are now automatically activated/deactivated.
  \item Hotkeys are now permanently set.
  \item For everyday work, use Tinn-R 0.0.9.0 r1.13
\end{itemize}


\subsection*{0.0.9.0 r1.13 (Jul/2004)}
\begin{itemize}
  \item Two new functions were added both to the \RR{} toolbar and the \RR{} menu:
    \textit{Print content of selected variable} and \textit{List names of selected variables}.
    Just experiment with these tools to figure out what they do (for instance,
    enter \textit{iris} in a .R file edited in Tinn-R and try these two tools while this word is selected).
  \item The icon for \textit{Help on selected word} was changed, and the \textit{Send file} icon in the \RR{}
    toolbar now has a transparent background.
  \item The \RR{} highlight dictionary was updated (about a hundred words were added).
\end{itemize}


\subsection*{0.0.9.0 r1.12 (Jun/2004)}
\begin{itemize}
  \item Bracket matching is reworked back to a more classical presentation: match brackets are now
    presented in bold and in a contrasting color (i.e., red if symbols are in a different color,
    or blue if symbols are colored in red).
  \item The prior content of the clipboard is now preserved in all \textit{Send to R} functions.
  \item Now the \RR{} console is completely cleaned when you use \textit{Clear all} (previously,
    commands to clear the console where left at the command line).
\end{itemize}


\subsection*{0.0.9.0 r1.11 (Jun/2004)}
\begin{itemize}
  \item Bug(s) fixed:
    \begin{itemize}
      \item Minor bug with match bracket was corrected.
    \end{itemize}
  \item On the menu \textit{Options/Application options} it is now possible to indicate if \RR{} resources
    are visible or not (switch between plain Tinn and Tinn-R).
  \item The menu \textit{Tinn to R} was renamed \textit{R}.
  \item Menu \textit{Tools} was reworked.  Tools/Initiate or Close preferred Rgui are now included in the \textit{R} menu.
  \item \textit{Copy Formatted} was added to the pop-up menu.
  \item Behavior of the \RR{} Toolbar was improved.
  \item Automatic match brackets was reworked: current bracket is shown surrounded by a red rectangle and previous match     brackets are shown surrounded by a background symbol color of the specific highlighter (user defined). Thus, if the active line is highlighted (Options/Application options) and the cursor is moved throughout a line of text with some brackets, it is now possible to identify which brackets have already been matched during the cursor move.
\end{itemize}


\subsection*{0.0.9.0 r1.10 (May/2004)}
\begin{itemize}
  \item Bug(s) fixed:
    \begin{itemize}
      \item Bugs with Search/Search in files/[x] Search in directories were corrected.
    \end{itemize}
  \item The Window of the results of the Search/Search in files can now be moved.
  \item Project interface was reformulated and pop-up menu is now available.
\end{itemize}


\subsection*{0.0.9.0 r1.09 (Mar/2004)}
\begin{itemize}
  \item Bug(s) fixed:
    \begin{itemize}
      \item Minor bugs with ControlBar (on resize for a lesser size that the
        ControlBar, close application and start new) and View/Toolbar
        (checked/unchecked) menu was corrected.
      \item A minor bug (Save/Save as) with associated extensions was corrected.
      \item A minor bug with hotkeys was corrected.
      \item A minor bugs with project was corrected.
      \item A minor bug with tollbar of macro was corrected.
    \end{itemize}
  \item Comment/Uncomment block was reformulated. This now work like
    Tinn-R 0.0.9.0.
  \item Two new hotkeys (not user configurable) were added:

    \begin{footnotesize}
      \begin{verbatim}
        <CTRL + ADD> key (numeric keypad)
        will insert/replace text with the attribution symbol '->';

        <CTRL + SUBTRACT> key (numeric keypad)
        will insert/replace text with the attribution symbol '<-'.
      \end{verbatim}
    \end{footnotesize}

  \item Search/Replace was improved. It is possible now to decide if the
    occurrence will be, or not, replaced.

    \begin{footnotesize}
      \begin{verbatim}
        Temporarily, and until a better solution is found, to work properly,
        if the window is horizontally split the Search/Replace must be  made
        at the bottom (main) window, because if it's at the top window (secondary)
        it doesn't question the confirmation to each substitution of the text occurrence.
        If the window is vertically split, the Search/Replace must be made at the
        left window (the right window does not question the confirmation to each
        substitution of the occurrence). For both, any key will synchronize the split windows.
      \end{verbatim}
    \end{footnotesize}

  \item Now Tinn-R can initiate (Tolls/Initiate ...) and close (Tolls/Close ...)
    preferred RGui. For the first, the path of preferred RGui must be previously
    set (Options/Application options).
  \item A new Tinn to \RR{} option was implemented: \textit{Help selected word}.
  \item Interface (appearance and icons) was reformulated.
  \item Tinn-R hotkeys' interface was reformulated. Now it is possible to choose
    the desired hotkeys to main actions.
  \item On the menu \textit{Options/Application options} it is possible to choose
    the appearance to Tinn-R like WinXP.
  \item It is possible to get the positions of Tinn-R toolbars (preserved) when
    application exits, and restore the next time it is started.
  \item On the (Edit/Copy formatted) it is possible to copy the native format
    and exported it in RTF, HTML and TeX format.
  \item Improvements were made to the highlighting.
  \item Now it is possible to open \textit{Projects} files with one mouse
    click.
\end{itemize}


\subsection*{0.0.8.9 r1.08 (Mar/2004)}
\begin{itemize}
  \item Bug(s) fixed:
    \begin{itemize}
      \item Small bug with Comment/Uncomment block was corrected.
    \end{itemize}
  \item Now Tinn-R also runs with R, SciViews-R and S-Plus (the last still not
    finalized but it is running if the window Commands or S-PLUS - [Commands]
    have the focus).
\end{itemize}


\subsection*{0.0.8.9 r1.07 (Feb/2004)}
\begin{itemize}
  \item Specific HotKeys (F1..F11) were implemented for all Tinn to \RR{}
    functions. If and while activated, they overlap all the HotKeys of
    the Windows and any application running.
  \item Tinn-R now generates the two files (Tinn.ini and Shortcuts.ini) on
    C:$\backslash$Documents and Settings$\backslash$\textit{UserName}$\backslash$Application Data
    (or Dados de aplicativos)$\backslash$Tinn$\backslash$.
  \item Upgrade Tinn 0.0.8.8 to 0.0.8.9 as
    \htmladdnormallink{changelog}{http://www.solarvoid.com/cgi-bin/viewcvs.cgi/TinnMDI/}.
  \item A few tweaks were made in brackets highlighting, as per Marco's suggestions.
  \item jcfaria suggested a little fix to the File Search window. Russ put it in.
  \item jcfaria suggested a change to the RegEx filter interface to check,
    to make sure the filter won't be blank before running it. Russ put that in.
  \item Marco suggested a few changes to the open procedure. Now it checks if the
    file is changed and allows the user to open the file or not.
  \item fLineWdith has been commented out.
  \item Marco also suggested a few changes to the Search In Files code. Russ put that in, too.
  \item Russ pulled out the bitmaps on a few buttons in a few dialogs as per Marco's suggestion to keep things unified.
\end{itemize}


\subsection*{0.0.8.8 r1.06 (Feb/2004)}
\begin{itemize}
  \item Bug(s) fixed:
    \begin{itemize}
      \item Bug = Assertion failure\\
        \begin{footnotesize}
          (c:$\backslash$arquivos de programas$\backslash$borland$\backslash$componentes$\backslash$synedit$\backslash$source$\backslash$SynEditWordWrap.pas, line149)
        \end{footnotesize}

        \begin{footnotesize}
          \begin{verbatim}
            Why and when?

            if you create a new file and type:

            <ENTER>
            and press <UP>  -> bug!

            This was corrected: thank you Marco Groot!
          \end{verbatim}
        \end{footnotesize}

    \end{itemize}
\end{itemize}


\subsection*{0.0.8.8 r1.05 (Feb/2004)}
\begin{itemize}
  \item Comment/uncomment block was implemented: default symbol used for the
    comment/uncomment must be set in Options/Application options.

    \begin{footnotesize}
      \begin{verbatim}
        Comment block   : Format/Comment block   <ALT+C>.
        Uncomment block : Format/Uncomment block <ALT+Z>.
      \end{verbatim}
    \end{footnotesize}

  \item Option of Format/Colunm was eliminated: it is better to use this
    options (when necessary) keeping ALT pressed. This options are
    set in Options/Editor Options/(x)Alt sets column modes.
  \item ShortCuts to Print and Play macro were set the same = \texttt{CTRL + P}:

    \begin{footnotesize}
      \begin{verbatim}
        F7 : new shortcut to Record Macro
        F8 : new shortcut to Play Macro.
      \end{verbatim}
    \end{footnotesize}

\end{itemize}
