
\hypertarget{2018}{}
\section{Versions released in 2018 (06)}
\index{What is New?!2018}

\subsection*{5.2.2.0 (oct/04/2018)}
\begin{itemize}
  \item Parts of the source code were enhanced.
  \item Some window and dialogs were reworked.
  \item The recognition of complex R object names for \texttt{search} and \texttt{search in files} were improved.
  \item Some keys from \texttt{INI file} were renamed to be more reliable:
    \begin{itemize} 
      \item \lbrack Roptions\rbrack $\to$ \lbrack R Options\rbrack
      \item \lbrack Options TextDiff\rbrack $\to$ \lbrack Diff Options\rbrack
      \item \lbrack PandocHistory\rbrack $\to$ \lbrack Pandoc History\rbrack
      \item \lbrack PandocHistoryFrom\rbrack $\to$ \lbrack Pandoc History From\rbrack
      \item \lbrack PandocHistoryTo\rbrack $\to$ \lbrack Pandoc History To\rbrack
      \item \lbrack SearchTextHistory\rbrack $\to$ \lbrack Search Text History\rbrack
      \item \lbrack SearchDirHistory\rbrack $\to$ \lbrack Search Dir History\rbrack
      \item \lbrack SearchFileMaskHistory\rbrack $\to$ \lbrack Search File Mask History\rbrack
      \item \lbrack ExplorerFavorites\rbrack $\to$ \lbrack Explorer Favorites\rbrack
      \item \lbrack FileMRU\rbrack $\to$ \lbrack File MRU\rbrack
      \item \lbrack ProjectMRU\rbrack $\to$ \lbrack Project MRU\rbrack
    \end{itemize}
    Therefore, some user preferences can be lost (when applicable, it will use the default values). Sorry for the incovenience.
\end{itemize}

\subsection*{5.2.1.0 (sep/28/2018)}
\begin{itemize}
  \item The main menu \texttt{Web/R(search)} were reworked.
  \item The recognition of complex R object names \texttt{for sending instructions} were improved.
\end{itemize}

\subsection*{5.1.6.0 (sep/26/2018)}
\begin{itemize}
  \item The \texttt{Application options} interface were reworked.
\end{itemize}

\subsection*{5.1.5.0 (sep/20/2018)}
\begin{itemize}
  \item Bug(s) fixed:
    \begin{itemize}
      \item A bug from the versions 5.1.3.0 and 5.1.4.0 (sep/20/2018) related to the demo project was fixed.
    \end{itemize}
\end{itemize}

\subsection*{5.1.4.0 (sep/20/2018)}
\begin{itemize}
  \item Bug(s) fixed:
    \begin{itemize}
      \item A bug from the version 5.1.3.0 (sep/20/2018) related to R scripts \texttt{utils/infor.R and install.R} was fixed.
    \end{itemize}
\end{itemize}

\subsection*{5.1.3.0 (sep/20/2018)}
\begin{itemize}
  \item Bug(s) fixed:
    \begin{itemize}
      \item A bug related to sending instructions when Rgui.exe was started out of Tinn-R was fixed.
      Thanks to \texttt{Allan Stewart-Oaten} for pointing it out.
    \end{itemize}
  \item A new button was added to the \texttt{Tools/R/Card} interface to open in the editor an example
  of the selected item.
  \item New resources were added to let Tinn-R access R remotely, via PuTTY.
    The way if working is the same as using Rgui.exe locally, but there are a few limitations.
  \item The interface \texttt{Options/Application/R} were reworked, and new options were added.
  \item The searching algorithm from the installers of R in the System Registry were remade. The problems issued
    by the non standardization after the installation of Microsoft R (MRAN), which were causing trouble in
    the correct identification of the installed versions were reworked.
\end{itemize}