
\hypertarget{2024}{}
\section{Versions released in 2024 (01)}
\index{What is New?!2024}

\subsection*{9.0.1.1 (Mar/31/2024)}
\textbf{Bug(s) fixed}
\begin{itemize}
   \item Possible failures in sending lines, when many lines - one by one - are sent to the \texttt{Term} interface
   (with the "|+" option checked) has been fixed. In other words, sending contiguous lines sequentially to the
   \texttt{Term} interface has been improved and is now more consistent. But you shouldn't abuse this feature either.
   Do not continually rest your finger on the shortcut key or hotkey defined for this action to send large quantities
   of lines, as there are better options for this purpose, with lower computational cost.
   \item A bug associated with the \texttt{Tools/R/Mirrors/Mirrors(R) update} button has been fixed.
    The issues that emerged with the new version of R (4.2.0 - UTF-8).
   \item Bug in changing the position of \texttt{tabs} of the \texttt{Main Interface}, \texttt{Options},
    \texttt{Tools} and \texttt{Term} has been fixed. From now on, all of them must only be in the \texttt{top}
    position.
   \item Fixed some \texttt{Term} interface bugs with the \texttt{knitr} package. The bugs arose due to
    changes in the sending patterns of R messages under the package, mainly if the progress bar option is
    checked (quiet=FALSE, which is the default). I hope the authors don't make drastic changes to the
    parsing progress messages to invalidate the regular expressions made to match the \texttt{Term}
    interface to the messages in the Knitr package.
   \item Bug associated to code completion has been fixed.
   \item Format XML, recognizes: .xml and .xsd.
   \item Bug in filtering in the \texttt{Tools/Database/Hotkeys} interface has been fixed.
\end{itemize}
   
\textbf{News}
\begin{itemize}
  \item Development was quite intense and uninterrupted throughout 2023.
   Only beta (or test) versions were released for a limited user base.
   The changes to the beta versions that occurred throughout the year were
   documented - collectively - only in this version.
  \item The user guide has been updated and improved.
  \item This is the latest compiled version of the project developed and compiled in the Delphi 2007 IDE.
   The project is in an advanced stage of migration to Embarcadero's new Delphi 11.3 (Alexandria) Community platform.
\end{itemize}

\textbf{Interface}
\begin{itemize}
  \item A new tab was created in \texttt{Tools/R} called \texttt{Working dir}.
   The objective is to allow a graphical visualization of the active R folder.
   It also allows storing favorites and indicating the work folder to R with several interesting options.
  \item \texttt{OpenURL} is a new option (in the \texttt{File} menu and taskbar) allows opening
   remote files in the editor.
  \item New options in the \texttt{Options/Application} interface make it possible to discover the program's
   reserved shortcuts. They cannot be changed by the user. There are few, but very important to know.
  \item Some buttons (somewhat redundant) were removed from the \texttt{Term} interface.
   It has become visually simpler.
  \item The \texttt{Tools} interface has been substantially improved.
  \item A new interface button \texttt{Tools/Windows expl.} and \texttt{Tools/Work expl.} allow physical
   deletion of displayed files.
  \item A small window was added in the \texttt{Tools/R explorer} interface that informs the
   description (.Rd) of each selected object.
  \item New (and useful) functions in the button (and corresponding menu) \texttt{R control: packages}.
  \item The indentation of the \texttt{Term/IO} interface has been improved. It was easier to read the
   submitted code due to the preservation of the script's original indentation.
  \item The \texttt{R Explorer} interface was improved.
  \item The \texttt{S/K/Hmanager} interface received updates and improvements.
  \item Change (hopefully for the better) in the alignment of texts in the Tools interface.
  \item \texttt{Tools/Completion} has been replaced by \texttt{Tools/Snippets}. The \texttt{Completion.xml}
   table is now named \texttt{Snippets.xml}. Users who have made (and saved) an extensive dataset of completion
   (before) (snippets from now on) will be able to notice a new button [\texttt{Merge (file .xml)}] that has been added
   in the new \texttt{Snippets} dialog window. When a new dataset (or any update to the source) is made,
   the user's dataset (\texttt{Completion.xml} or \texttt{Snippet.xml}, respectively) is saved in the \textbf{bkp} folder which is located
   in the Tinn-R startup folders (\texttt{Help/Ini files (path information)}). The new button allows the user's old base
   (completion or snippets) to be merged with the current one distributed with the new versions and eventually
   modified at the source. Thanks to Ivan B. Allaman for the helpful suggestion.
  \item Replacement and addition of many icons has been made.
  \item Filters can be applied to virtually all database-related features in the Tools interface:
  \begin{itemize}
    \item Database: \texttt{Shortcuts (app)}, \texttt{Keystrokes (editor)}, \texttt{Hotkeys (R)},
     \texttt{Snippets}, \texttt{Comments}, \texttt{Card} and \texttt{Mirrors}.
  \end{itemize}
  \item Possibility of controlling the transparency of main and secondary windows independently.
  \item The \texttt{Options} interface has been improved.
  \item New resizing options in the \texttt{Term/LOG} interface.
  \item The \texttt{Web} menu item received updates and improvements.
  \item New options in the popup menu associated with projects allow sending files \texttt{Rnoweb}
   (\texttt{Rnw}, \texttt{Rmd} and \texttt{RHtml}) (via \texttt{Sweave} and \texttt{knit})
   directly to be interpreted, without being open.
\end{itemize}
   
\textbf{Code}
\begin{itemize}
  \item Many efforts have been made in improving, standardizing and optimizing the source code.
  \item \texttt{Tip} and \texttt{Snippets} received updates and improvements.
  \item Dynamic updating of \texttt{R mirrors} has been improved.
\end{itemize}
       
\textbf{Packages}
\begin{itemize}
  \item The \texttt{TinnRcom} package has been improved and has new functions. These functions are
   associated with searching for information in the documentation (.Rd) of objects.
  \item Updated dependencies of package \texttt{TinnRcom}.
\end{itemize}
   
\textbf{New features}
\begin{itemize}
  \item Built a (new) search interface for \texttt{Snippets} triggers: thanks to \texttt{Ivan B. Allaman}
   for the suggestion.
  \item A (new) search interface was built with information linked to the documentation (.Rd) of the objects.
  \item Implemented search and replace in the \texttt{Term/IO} and \texttt{Term/LOG} interface.
  \item The \texttt{Snippets} (and respective search interface) are also functional in the \texttt{Term} interface.
\end{itemize}
   
\textbf{Database}
\begin{itemize}
  \item Practically all database tables were updated.
\end{itemize}
   
\textbf{Changes to shortcuts}
\begin{itemize}
  \item Shortcuts (app)
  \begin{itemize}
    \item \texttt{Ctrl + L}: In the \texttt{Term} interface clears the \texttt{IO} and \texttt{LOG} windows
    \item \texttt{Alt + Space}: Find again
  \end{itemize}
  \item The default hotkeys for R have been changed.
\end{itemize}
