
\hypertarget{2019}{}
\section{Versions released in 2019 (05)}
\index{What is New?!2019}

\subsection*{5.4.1.1 (to be released)}
\begin{itemize}
  \item We are looking for the maximum freedom and efficiency to interact with the R interpreter.
    In this sense, improvements have been made to the \texttt{Rterm IO} interface and some of the restrictions
    on editing inside of this interface (mainly related to last line or the prompt) have been removed.
  \item From now, to send any line (or just one small selection) to the R interpreter, you must press the
    \textbf{CTRL + ENTER} shortcut keys (not user configurable). \textit{It is not recommended to send selection of more than one line of code in this way}.
  \item The \texttt{R history} can be viewed (and searched) in a new synEdit completion window. The shortcut (not user configurable) is \textbf{CTRL + ALT + SPACE}.
  \item The \texttt{R highlighter} was improved, has new objects and from now it is case dependent, it is, it will highlighter, for example
    \textbf{LETTERS, letters, CO2, co2, \ldots} in the same way.
  \item Some parts of the Object Pascal \textbf{pipe} were rewritten.
  \item From this version the instructions stored in \texttt{R history} are only those typed and submitted directly in the \texttt{Rterm IO} interface.
  \item The highlighter identifier \texttt{Note} was renamed to \texttt{Note\_0}. It make more sense since it were created \texttt{Note\_1} and \texttt{Note\_2}
    in previous version.
\end{itemize}

\subsection*{5.3.4.1 (apr/22/2019)}
\begin{itemize}
  \item Two new identifiers have been added to highlighters
   \textbf{R} and \textbf{Text}: \texttt{Note\_1} and \texttt{Note\_2}.
   They are useful to be used as differentiated marks (now in three levels) in scripts and texts.
\end{itemize}

\subsection*{5.3.3.1 (fev/25/2019)}
\begin{itemize}
  \item Bug(s) fixed:
    \begin{itemize}
      \item A bug associated to the procedure \texttt{Help/Check for update} and the prior
        \texttt{5.3.2.1 (fev/12/2019) portable} version was fixed.
    \end{itemize}
\end{itemize}

\subsection*{5.3.2.1 (fev/12/2019)}
\begin{itemize}
  \item The recognition of complex R object names for \texttt{print}, \texttt{plot}, \texttt{names}
    \texttt{structure}, \texttt{edit}, \texttt{fix}, \texttt{help}, \texttt{example} and \texttt{open example}
      were improved. For example, to all cases:
    \begin{itemize}
      \item iris
      \item iris[1]
      \item iris[c(1, 2)]
      \item iris3(1, 1, 3)
      \item iris\$Sepal.Length
      \item iris['Sepal.Length']
      \item iris[["Sepal.Length"]]
    \end{itemize}
    that it will be correctly recognized.
  \item The \texttt{Replace} procedure was improved. From now it will remember, for all files, the same
    word list used to replacement.
  \item The \htmladdnormallink{Tinn-R web site}{https://nbcgib.uesc.br/tinnr/en/} was updated,
    the new URL is: \textbf{https://nbcgib.uesc.br/tinnr/en/}.
\end{itemize}

\subsection*{5.3.1.1 (jan/06/2019)}
\begin{itemize}
  \item The status bar was redesigned.
  \item The option \texttt{R send: line} have a new feature that allows the main editor to send sequential instructions
    while the interpreter returns the signal +(plus) after each incomplete instruction. This option can be fast and easily switched in the status bar.
  \item A new option to send instructions to R interpreter is being implemented: \texttt{R send: smart}.
    The goal is to simplify to begginer users to send complete instruction blocks when the cursor is located in a complex context:
    Out of the first line of functions, instructions with several contiguous lines and similar situations.
    The work is advanced, but not yet fully done. Because of that, this feature is disabled. If the user try to use/enable it, will get the message:
    \texttt{This feature is still in development.}
  \item The interface \texttt{Hotkeys (operational system)} were simplified and improved. Additionally, the amount of customizable user actions
    was increased to 20. On demand, this number can be easily increased.
    Due to this changes, the previous hotkeys will be lost and it is necessary to recreate them from the new GUI.
  \item Excepting the source files of Project Description (\texttt{Tinn\_R.dpr} and \texttt{Tinn-R\_portable.dpr}),
   all source code files were unified. Therefore, from now on it became easier to compile and distribute the
   \texttt{setup} e \texttt{portable} \texttt{Tinn-R\_X.X.X.X\_setup.exe} and \\
   \texttt{Tinn-R\_X.X.X.X\_portable.zip} versions, respectively.
   The custom support in PortableApps standards were completely removed.
  \item From this version it is possible to use some special characters
    (for example: \textbf{.aa}, \textbf{-bb}, \textbf{\_cc}, \textbf{~dd}, \textbf{?ee} \textbf{!ff} and \textbf{@gg}) as trigger to data completion.
    All triggers of the new HTML group begin with \textbf{'<'} character. It will give more flexibility to create completion to other languages.
  \item The mechanism of completion was enhanced a bit. From now on it is more user friendly related to the indentation of the text in all supported languages.
  \item Corrections were made in the popup menu interfaces \texttt{Rterm} \texttt{IO} and \texttt{LOG}.
  \item The option to donate to the project has changed. From now on it will be a bank account in the name of project coordinator.
    \textbf{Please, do not use the PayPal account anymore}.
\end{itemize}