
\chapter*{About the Author and Collaborators}
\addcontentsline{toc}{chapter}{About the Author and Collaborators}


\textbf{AUTHOR}: \\
\textbf{Faria, José Cláudio}
teaches statistics at Universidade Estadual de Santa Cruz - UESC \\
(Santa Cruz State University), Bahia/Brazil. \\
He is head of the Laboratory of Computational Statistics - \href{https://lec.pro.br/}{LEC}. \\
%\href{http://www.uesc.br/en/}{URL}: http://www.uesc.br/en/ \\

\vspace{0.5cm}

\textbf{COLLABORATORS}: \\
\textbf{Grosjean, Philippe}
teaches biostatistics and aquatic ecology at Mons University, UMONS, Belgium. \\
He is head of the Laboratory of Numerical Ecology of Aquatic Systems at UMONS. \\
%\href{http://econum.umons.ac.be/labo/}{URL}: http://econum.umons.ac.be/labo/ \\

\textbf{Jelihovschi, Enio Galinkin}
teaches statistics at Universidade Estadual de Santa Cruz - UESC \\
(Santa Cruz State University), Bahia/Brazil. \\
%\href{http://www.uesc.br/en/}{URL}: http://www.uesc.br/en/ \\

\textbf{Pietrobon, Ricardo}
is Associate Vice Chair and Associate Professor, Department of Surgery,
Research on Research Group, Duke University Medical Center. \\
%\href{http://researchonresearch.duhs.duke.edu}{URL}: http://researchonresearch.duhs.duke.edu \\

\textbf{Farias, Philipe Silva}
is a Computer Science student at Universidade Estadual de Santa Cruz - UESC \\
(Santa Cruz State University), Bahia/Brazil. \\
%\href{http://www.uesc.br/cursos/graduacao/bacharelado/ciencia_da_computacao/index.php}{URL}: http://www.uesc.br/cursos/graduacao/bacharelado/ciencia\_da\_computacao/index.php \\

\textbf{Kramer, Philiphe Alexandre Ribeiro}
is graduated in Computer Science at Universidade Estadual de Santa Cruz - UESC \\
(Santa Cruz State University), Bahia/Brazil. \\
%\href{http://www.uesc.br/cursos/graduacao/bacharelado/ciencia_da_computacao/index.php}{URL}: http://www.uesc.br/cursos/graduacao/bacharelado/ciencia\_da\_computacao/index.php \\

\textbf{Farnese, Balthazar Mattos}
is an independent WEB developer hired to maintain the \href{https://lec.pro.br/}{Tinn-R Website}. \\
Ilhéus, Bahia/Brazil. \\
